Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-10-31 robdml.tex
tex

\noindent\textbf{I. Effectivenss of Hardness Manipulation}.

@@

To figure out the efficacy of HM with $H_\mathcal{D}$ calculated from benign
triplets, we adversarialy train models dataset using $\text{HM}[\mathcal{R},
\mathcal{M}]$ and $\text{HM}[\mathcal{S}, \mathcal{M}]$ on the CUB dataset,
with varying PGD steps, \ie, $\eta\in\{2,4,8,16,32\}$, respectively.
%
The results can be found in \cref{tab:hmeff}.
%
The performance of the state-of-the-art defense, \ie, ACT~\cite{robrank} is
also provided as a baseline.
%
ACT[$\mathcal{R}$] and ACT[$\mathcal{S}$] mean the training triplet is sampled
using Random and Softhard strategy, respectively.
%
We also plot curves in \cref{fig:hmeff} based on the robustness, training
cost\footnote{Training cost is the number of times for forward and backward
propagation in each adversarial training iteration, which is calculated as
$\eta+1$.}, as well as the R@1 performance on benign examples to reflect the
characteristics of these methods.

@@

@@

\noindent\textbf{II. Effectiveness of Gradual Adversary}.

\begin{figure}[t]
	\includegraphics[width=\columnwidth]{figgaeff.pdf}
	\caption{GA eff}
\end{figure}

\begin{figure}[t]
	\includegraphics[width=\columnwidth]{figics.pdf}
	\caption{ICS eff}
\end{figure}

\input{tab-gaeff.tex}

@@

\input{tab-ics.tex}

Put together for easier comparison.

\noindent\textbf{III. Effectivenss of Intra-Class Structure}.

>>>>

@@

\noindent\textbf{I. Hardness Manipulation.}
%
To validate HM with $H_\mathcal{D}$ calculated from benign
triplets, we adversarially train models using $\text{HM}[\mathcal{R},
\mathcal{M}]$ and $\text{HM}[\mathcal{S}, \mathcal{M}]$ on the CUB dataset,
with varying PGD steps, \ie, $\eta\in\{2,4,8,16,32\}$, respectively.
%
The results can be found in \cref{tab:hmeff}.
%
The performance of the state-of-the-art defense, \ie, ACT~\cite{robrank} is
provided as a baseline.
%
ACT[$\mathcal{R}$] and ACT[$\mathcal{S}$] mean the training triplet is sampled
using Random and Softhard strategy, respectively.
%
We also plot curves in \cref{fig:hmeff} based on the robustness, training
cost\footnote{Training cost is the number of times for forward and backward
propagation in each adversarial training iteration, which is calculated as
$\eta+1$.}, as well as the R@1 performance on benign examples.

@@

\input{tab-gaeff.tex}
\input{tab-ics.tex}

@@

\begin{figure}[t]
	\vspace{-1em}
	\includegraphics[width=\columnwidth]{figgaeff.pdf}
	\vspace{-1.5em}
	\caption{GA eff}
\end{figure}

\begin{figure}[t]
	\vspace{-1em}
	\includegraphics[width=\columnwidth]{figics.pdf}
	\vspace{-1.5em}
	\caption{ICS eff}
\end{figure}

\noindent\textbf{II. Gradual Adversary.}

@@

\noindent\textbf{III. Intra-Class Structure.}

\cref{tab:ics}
